Comparative Analysis of Approximation Algorithms for Solving TSP

### 2018-04-28 tex/paper.tex
Add machine spec and Octave version

	The codes to solve the TSP\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. The generated path efficiency is calculated as the percentage of the increase in the resulting path length over the optimal path.
	$\frac{\textit{Detected Path Length} - \textit{Optimal Path Length}}{Detected Path Length} * 100 $

>>>>

	The codes to solve the TSP\cite{Kirk14}\cite{mathwork}\cite{Jang02}\cite{Jevtic14}\cite{Ibrahim15} were executed on both Matlab and Octave V4.0 using Intel i7-2630QM with 4 cores and 6Gb of RAM aand running on Ubuntu 16.04 Linux-kernel 4.4.0-119-generic, taking into consideration the resulting output path length and the execution time. All the test conducted were repeated ten times each in order to see how well the algorithms can improve in both criteria. The generated path efficiency is calculated as the percentage of the increase in the resulting path length over the optimal path.
	$\frac{\textit{Detected Path Length} - \textit{Optimal Path Length}}{Detected Path Length} * 100 $
